---
title: "Lab 10"
author: "Derek Maldonado"
date: "11/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results:
Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867
Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests
Reproduce a graph of the means, like shown in the paper
Present a power-curve analysis for the design


```{r}
library(papaja)
library(dplyr)
library(ggplot2)
library(tidyr)

data1 <- read.csv(file="lab10data/standbystroop.csv")

stand3 <- t.test(data1$incongruent_stand,
       data1$congruent_stand,
       paired = TRUE)
sit3 <- t.test(data1$incongruent_sit,
       data1$congruent_sit,
       paired = TRUE)



stroop_df <- data1 %>%
  pivot_longer(cols = 2:5,
               names_to = c("Congruency","Posture"),
               names_sep = "_",
               values_to = "RTs")


overall_means <- stroop_df %>%
                  group_by(Posture,Congruency) %>%
                  summarise(meanRT = mean(RTs),
                            SEMRT = (sd(RTs)/sqrt(length(RTs))))


ggplot(overall_means, aes(x=Posture,
                          y=meanRT, 
                          group=Congruency,
                          fill=Congruency))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(500,1000))

# 50% did first part alone, struggled with graph

```

The Stroop effects in both the sitting condition, `r papaja::apa_print(sit3)$full_result`, and the standing condition, `r papaja::apa_print(stand3)$full_result`, were highly reliable according to the retest complete


## power curve

```{r}
effects <- seq(0,1.5,.1)
proportion <-c()
for(i in 1:length(effects)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effects[i], 1)),
                                   mu = 0)$p.value)
  
  proportion[i] <- length(sim_ps[sim_ps < .05])/1000
}
plot_df <- data.frame(effects,
                      proportion)
ggplot(plot_df, aes(x=effects,y=proportion))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Percentage of Proportion Significant")

# 5% struggled with this, been very long since class when we covered this
```
