---
title: "lab11"
author: "Derek Maldonado"
date: "12/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
An X and Y variable contain the given numbers.
A. Compute Pearson’s r and report the associated p-value using the cor.test() function.
B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution.

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
# A
q1ans <- cor.test(X,Y)
q1ans$p.value

#B
library(ggplot2)
library(ggrepel)

simnull <- replicate(1000,cor(sample(X),sample(Y)))
hist(simnull)
length(simnull[simnull >= cor(X,Y)])/1000

#100%

```



## Question 2
Using the variables X and Y given, and assuming that the values could be re-ordered in any way, report the following:
A. the smallest possible sum of cross-products
B. the largest possible sum of cross-products

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)

xmax <- sort(X)
ymax <- sort(Y)
ansB <- sum(xmax*ymax)

ymin <- sort(Y, decreasing = TRUE)
ansA <- sum(xmax*ymin)



#answer for A
ansA
#answer for B
ansB

#100%
```


