---
title: "Lab8"
author: "Derek Maldonado"
date: "10/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.
Advanced: 
Have an option so that the function will convert the raw scores to zscores in one of two ways:
using user provided mean and standard deviation
using the calculated mean and standard deviation from the raw scores



```{r}
library(dplyr)
library(ggplot2)

r2z <- function(scores, mu, sd){
  zscore <- (scores-mu)/sd
  return(zscore)
}

scores <- c(1:10)
mu <- 3
sd <- 1
r2z(scores,mu,sd)


#100% straightforward enough
```

## Including Plots



```{r}
ztest <- function(scores, mu, sd){
  xbar <- mean(scores)
  zscore <- ((xbar-mu)/sd)
  
}


scores <- c()


```





