---
title: "Lab9"
author: "Derek Maldonado"
date: "November 11, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1.
Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did

```{r}
library(dplyr)
library(tidyr)

data1 <- read.csv(file="lab9data/infantchoosingdata.csv")


ex1data <- data1 %>%
  filter(ExperimentNumber == "1")

sumofchoices <- sum(ex1data$Infant.Chose.C)
amountofchoices <- length(ex1data$Infant.Chose.C)
(binomial1 <- pbinom(q = amountofchoices - sumofchoices,
                      size = amountofchoices, 
                      prob = .5, 
                      lower.tail = TRUE)*2)

gender_choice_table <- ex1data %>%
  group_by(Gender, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[,2:3]
(gender_Xsq <- chisq.test(gender_choice_table))  

uncorrected_Xsq <- sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)
gender_Xsq_unc <- pchisq(uncorrected_Xsq,1,lower.tail = FALSE)

age_table <- ex1data %>%
  group_by(AgeMonths, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(AgeMonths),
              values_from = counts)
age_table[is.na(age_table)] <- 0
age_table <- as.matrix(age_table[,2:21])
(age_xs <- chisq.test(age_table))

#20% I constantly struggle with the filtering (%>%) and specifying ($) of the data i'm working with. I need to get the hang of that.

```
I did the exact same experiment as the paper's authors and received the same scores, even if one had errors on their part. 

