---
title: "StatsLab1"
author: "Derek Maldonado"
date: "8/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Compute the sum of the sequence 100 to 1000, going up by a constant value of 100 (100,200,300,400,500,600,700,800,900,1000).


```{r}
sum(1:100)
```

## Question 2
Compute the sum of these numbers (1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5)


```{r}
sum(c(1,3,2,4,3,5,4,3,4,5,6,5,6,7,6,5,6,5,4,3,4,5))
```

## Question 3
Write a custom sequence generator function using a for loop that generates a sequence from a starting integer value to an ending integer value in steps of 1. Demonstrate that it can produce the ?con?sequence 1 to 10.


```{r}
i <-1
while(i<11) {
  print(i)
  i=i+1
}
```


## Question 4
Write a custom function to implement the general equation to find the sum of any constant series


```{r}
stat_function <- function(X1, Xn, c){
  temp <- ((((Xn-X1)/c)+1)*((X1+Xn)/2))
  return(temp)
}
#Xn is ending number
#X1 is starting number
#c is number we count by
stat_function(10,100,10)
```

## Question 5
Write a custom function that generates a constant series between any start and end values, with any constant, and finds the sum. Have the function output both the sequence and the sum. For this problem, feel free to use the existing functions in the custom function. Demonstrate the function correctly prints out the above sequence (10 to 100 by 10), and its sum


```{r}
fun2 <- function(xs, xf, d){
  temp <- (sum (seq(xs, xf, d)))
  print(seq(xs, xf, d))
return (temp)
}
#xs is starting number
#xf is final number
#d is counting by
fun2(10,100,10)
```


## Question 6
Use the sum() and the length() functions to calculate the mean (average) of the numbers x = c(1,2,3,4,5).

```{r}
e <- c(1,2,3,4,5)
s_e <- sum(e)
l_e <- length(e)
answer <- s_e/l_e
print(answer)
```
